Extracting data for time slice analyses

### 2017-11-23 analyses/01-extract-data-for-analyses.Rmd
Add processing code for other datasets

@@

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
```
Bapst et al 2016 Biol Letters
-----------

>>>>

Heath et al bears
-----------

```{r}
slug <- "bears"

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)
tree <- read.nexus(paste0("../data/trees/", slug, ".nex"))

Brusatte et al 2014 Current Biol
-----------

```{r}
slug <- "Brusatte2014"

@@
